On The Impact of Atoms of Confusion in JavaScript Code

### 2021-04-05 4_Result.tex
Updates from Overleaf

\subsubsection*{The Participants' perceptions of the atom candidates}
Supporting the results of the survey, Table~\ref{tab:interview-results1}
 shows that for eight out of the
nine scenarios surveyed, the maijority of the respondents agree that the version of the
code without the atom of confusion is easier to understand, and in no case the \emph{neutral}
ratio was higher than the option for the version without atoms of confusion.
%% An example entry is contained in Appendix~\ref{}. 
%% For a full listing of the code snippets, visit the paper repository. 
Only for the Ternary Operator atom candidate the participants
prefer the version of the code with the atom of confusion,
instead of the more cleaner version without the atom of confusion.
Even in this case, some participants who opted for
the \emph{left-hand-side} (with the atom of confusion) version
still believed that the \emph{right-hand-side} (without the atom of
confusion) version was more readable (see Figure~\ref{code:ternary}). 
The following quotes were extracted from the transcripts with
three interviewees:

>>>>

\subsubsection*{The Participants' perceptions of the atom candidates}
Supporting the results of the survey, Table~\ref{tab:interview-results1}
 shows that for eight out of the
nine scenarios surveyed, the majority of the respondents agree that the version of the
code without the atom of confusion is easier to understand, and in no case the \emph{neutral}
ratio was higher than the option for the version without atoms of confusion.
%% An example entry is contained in Appendix~\ref{}. 
%% For a full listing of the code snippets, visit the paper repository. 
Only for the Ternary Operator atom candidate the participants
prefer the version of the code with the atom of confusion,
instead of the more cleaner version without the atom of confusion.
Even in this case, some participants who opted for
the \emph{left-hand-side} (with the atom of confusion) version
still believed that the \emph{right-hand-side} (without the atom of
confusion) version was more readable (see Figure~\ref{code:ternary}). 
The following quotes were extracted from the transcripts with
three interviewees:
